Every Author as First Author

### 2023-03-27 paper.tex
Fix for long author list
Remove ACM from copyright
Bib fixes
Opacity subsection

{\makeatletter \gdef \@copyrightdata {\hspace{-2.5em}\protect\namestack{Erik D. Demaine; Martin L. Demaine}}}

%
% the following standard packages may be helpful, but are not required
%
\usepackage{courier}            % standard fixed width font
\usepackage[scaled]{helvet} % see www.ctan.org/get/macros/latex/required/psnfss/psnfss2e.pdf
\usepackage{url}                  % format URLs
\usepackage{listings}          % format code
\usepackage{enumitem}      % adjust spacing in enums
\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false]{hyperref}   % hyperlinks, including DOIs and URLs in bibliography
% known bug: http://tex.stackexchange.com/questions/1522/pdfendlink-ended-up-in-different-nesting-level-than-pdfstartlink
\newcommand{\doi}[1]{doi:~\href{http://dx.doi.org/#1}{\Hurl{#1}}}   % print a hyperlinked DOI

@@

To improve legibility, we write each name in semi-transparent ink
(currently, $2/3$ opacity).  Compare:
%
\begin{itemize}
\item Opacity $1$\phantom{${}/1$}:
  \texttransparent{1}{\textstack{Erik Demaine; Martin Demaine}}
\item Opacity $3/4$:
  \texttransparent{0.75}{\textstack{Erik Demaine; Martin Demaine}}
\item Opacity $2/3$:
  \texttransparent{0.666}{\textstack{Erik Demaine; Martin Demaine}}
\item Opacity $1/2$:
  \texttransparent{0.5}{\textstack{Erik Demaine; Martin Demaine}}
\end{itemize}
%
In the future, we may consider using a different opacity depending on the
number of authors.  More extremely, we could use opacity to indicate the
relative contribution of each author (when they are unequal), or different
colors to represent different roles (such as supervisor).

@@

\bibliography{paper}
\bibliographystyle{overlap-abbrvnat}

>>>>

{\makeatletter \gdef \@copyrightdata {\hspace{-2.5em}%
  \rlap{\textcolor{white}{\rule{2.5em}{1em}}}%
  \protect\namestack{Erik D. Demaine; Martin L. Demaine}}}

%
% the following standard packages may be helpful, but are not required
%
%\usepackage{courier}            % standard fixed width font
\usepackage[scaled]{helvet} % see www.ctan.org/get/macros/latex/required/psnfss/psnfss2e.pdf
\usepackage[hyphens,spaces,obeyspaces]{url}
\usepackage{listings}          % format code
\usepackage{enumitem}      % adjust spacing in enums
\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false]{hyperref}   % hyperlinks, including DOIs and URLs in bibliography
% known bug: http://tex.stackexchange.com/questions/1522/pdfendlink-ended-up-in-different-nesting-level-than-pdfstartlink
\newcommand{\doi}[1]{doi:~\href{http://dx.doi.org/#1}{\Hurl{#1}}}   % print a hyperlinked DOI

@@

\subsection{Opacity}

To improve legibility, we write each name in semi-transparent ink
(currently, $2/3$ opacity).
As a result, where multiple characters overlap, the ink appears darker,
making the names more legible.%
%
\footnote{Warning: Not all PDF viewers correctly display text transparency
  as created by \texttt{transparent.sty}.  Notably, Adobe Acrobat on Windows
  does not seem to darken where multiple layers overlap.}
%
Compare:
%
\begin{itemize}
\item Opacity $1$\phantom{${}/1$}:
  \texttransparent{1}{\textstack{Erik Demaine; Martin Demaine}}
\item Opacity $3/4$:
  \texttransparent{0.75}{\textstack{Erik Demaine; Martin Demaine}}
\item Opacity $2/3$:
  \texttransparent{0.666}{\textstack{Erik Demaine; Martin Demaine}}
\item Opacity $1/2$:
  \texttransparent{0.5}{\textstack{Erik Demaine; Martin Demaine}}
\end{itemize}
%
In the future, we may consider using a different opacity depending on the
number of authors.  More extreme, we could use opacity to indicate the
relative contribution of each author (when they are unequal), or different
colors to represent different roles (such as supervisor).
But for now we like the uniformity of every name
appearing the same in all contexts.

@@

\bibliography{paper}
\bibliographystyle{stack-abbrvnat}
